---
title: "midterm extra"
author: "Kushal"
date: "11/10/2021"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Cancer: 9.51:Wilcoxon Rank Sum Test
#9.52
```{r}
data1 = read.table("data2.csv", header = TRUE, sep=",")
summary(data1)
by(data1$serum, data1$group, summary)
wilcox.test(data1$serum~data1$group)
```
Ho: median(Caucasian)= median(African-American)
Ha: median(Caucasian) is not equal to median(African-American)
Test Statistic: W*= 86
P-value: 0.5599
Conclusion (at the .05 level): Fail to reject Ho. Here p-value is greater than (alpha=0.05). So,there is not sufficient evidence to reject that the median of the Caucasian is equal to the median for the African-American.


#7.4.3
```{r}
pre <- c(29.8,73,98.6,58.8,60.6,57.2,57.2,89.2,97,49.8,37)
post  <- c(57.2,69.8,98.2,62.4,67.2,70.6,67.8,95.6,98.4,63.2,63.6)
difference <- pre - post
summary(difference)
shapiro.test(difference)
```
Assumptions:
Ho: Data are normally distributed.
Ha: Data are not normally distributed
 
Test statistic: W*= 0.90999

P-value: 0.2438

Conclusion: Fail to reject Ho. The p-value is greater than (alpha=0.05).There is insufficient evidence to reject Ho. So we cannot say that difference is not normally distributed.
```{r}
t.test(pre,post,paired=TRUE)
```
Ho: Mean(Methadone group)=Mean(Placebo)

Ha: Mean(Methadone group) is not equal to Mean(Placebo)
 
Test statistic: t* = -3.1554

P-value: 0.01024

Conclusion : Reject Ho in favor of Ha. Here,p-value is less than (alpha=0.05). So there is sufficient evidence to say that Mean(Methadone group) is not equal to Mean(Placebo)


#Obstetrics
#12.14
```{r}
lengthdata = read.table("data1.csv",header=TRUE,sep=",")
dim(lengthdata)
head(lengthdata)
is.factor(lengthdata$location)
is.factor(lengthdata$code)
lengthdata$code = factor(lengthdata$code)
is.factor(lengthdata$code)
model1 <- aov(birthweig~code, data=lengthdata)

uhat<-resid(model1)

qqnorm(uhat)

shapiro.test(uhat)
```


Ho: Residuals normally distributed
Ha: Residuals not normal distributed
Test Statistic: W*= 0.97039
P-value: 0.6121
Conclusions: Fail to reject Ho.We do not have suficient evidence to prove that the residuals are not normally distributed.

```{r}
summary(model1)
```
Ho: All means are equal
Ha: at least one mean differs
Test Statistic: F*= 6.258
P-value: 0.0029
Conclusions: Reject Ho in favor of Ha. We have sufficient evidence to prove that at lease one mean birthweights differs from the group.

```{r}
TukeyHSD(model1, conf.level = 0.95)

```


#6.75
```{r}
patient <- c(2,6,9,33,49,66,52,37,18,11,4)
mean(patient)
sd(patient)
n <- length(patient)
n
se <- sd(patient)/sqrt(n)
mean(patient) + qt(c(0.025, 0.975), n-1) * se
ci <- mean(patient) + qt(c(0.025, 0.975), n-1) * se
```
